---
title: "R Notebook - kaggle credit default risk"
output: html_notebook
---

```{r}
setwd("/Users/praneesh/Downloads/All")
```


```{r}
# General 
library(tidyverse)
library(skimr)

# Preprocessing
library(recipes)

# Machine Learning
library(h2o)

```

```{r}
application_train_tbl <- read_csv("application_train.csv")
application_test_tbl  <- read_csv("application_test.csv")
```


```{r}
application_train_tbl %>%
    slice(1:10) %>%
    knitr::kable()
```

```{r}
# Training data: Separate into x and y tibbles
x_train_tbl <- application_train_tbl %>% select(-TARGET)
y_train_tbl <- application_train_tbl %>% select(TARGET)   

# Testing data: What we submit in the competition
x_test_tbl  <- application_test_tbl

# Remove the original data to save memory
rm(application_train_tbl)
rm(application_test_tbl)
```

```{r}
skim_to_list(x_train_tbl)
```

```{r}
string_2_factor_names <- x_train_tbl %>%
    select_if(is.character) %>%
    names()

string_2_factor_names
```

```{r}
unique_numeric_values_tbl <- x_train_tbl %>%
    select_if(is.numeric) %>%
    map_df(~ unique(.) %>% length()) %>%
    gather() %>%
    arrange(value) %>%
    mutate(key = as_factor(key))

unique_numeric_values_tbl
```

```{r}
factor_limit <- 7

num_2_factor_names <- unique_numeric_values_tbl %>%
    filter(value < factor_limit) %>%
    arrange(desc(value)) %>%
    pull(key) %>%
    as.character()

num_2_factor_names
```

```{r}
missing_tbl <- x_train_tbl %>%
    summarize_all(.funs = ~ sum(is.na(.)) / length(.)) %>%
    gather() %>%
    arrange(desc(value)) %>%
    filter(value > 0)

missing_tbl
```

```{r}
#Preprocessing Implementation And H2O Modeling
rec_obj <- recipe(~ ., data = x_train_tbl) %>%
    step_string2factor(string_2_factor_names) %>%
    step_num2factor(num_2_factor_names) %>%
    step_meanimpute(all_numeric()) %>%
    step_modeimpute(all_nominal()) %>%
    prep(stringsAsFactors = FALSE)

rec_obj
```

```{r}
#bake in the transformations into the train and test sets
x_train_processed_tbl <- bake(rec_obj, x_train_tbl) 
x_test_processed_tbl  <- bake(rec_obj, x_test_tbl)
```

```{r}
# Before transformation
x_train_tbl %>%
    select(1:30) %>%
    glimpse()
```

```{r}
# After transformation
x_train_processed_tbl %>%
    select(1:30) %>%
    glimpse()
```

```{r}
y_train_processed_tbl <- y_train_tbl %>%
    mutate(TARGET = TARGET %>% as.character() %>% as.factor())
```

```{r}
rm(rec_obj)
rm(x_train_tbl)
rm(x_test_tbl)
rm(y_train_tbl)
```

```{r}
h2o.init()
```

```{r}
h2o.no_progress()
```

```{r}
data_h2o <- as.h2o(bind_cols(y_train_processed_tbl, x_train_processed_tbl))
```

```{r}
splits_h2o <- h2o.splitFrame(data_h2o, ratios = c(0.7, 0.15), seed = 1234)

train_h2o <- splits_h2o[[1]]
valid_h2o <- splits_h2o[[2]]
test_h2o  <- splits_h2o[[3]]
```

Creating target encoding map on ORG_TYPE

```{r}
train_h2o$fold <- h2o.kfold_column(train_h2o, 5, seed = 1234)
te_map <- h2o.target_encode_create(train_h2o, x = list("ORGANIZATION_TYPE"),
                                   y = TARGET, fold_column = "fold")
head(te_map$ORGANIZATION_TYPE)
```

Apply the target encoding to the training and test data sets. Use the following param for the training data:
holdout_type" "KFold"
blended_avg: TRUE
noise_level: NULL(by default it will add 0.01 * range of y of random noise)

```{r}
ext_train_h2o <- h2o.target_encode_apply(train_h2o, x = list("ORGANIZATION_TYPE"), y = TARGET,
                                     target_encode_map = te_map, holdout_type = "KFold",
                                     fold_column = "fold",
                                     blended_avg = TRUE, noise_level = 0, seed = 1234)

head(ext_train_h2o[c("ORGANIZATION_TYPE", "fold", "TargetEncode_ORGANIZATION_TYPE")])
```

For the validation & testing data, use the parameters:
holdout_type: “None”
blended_avg: False
noise_level: 0

```{r}
ext_valid_h2o <- h2o.target_encode_apply(valid_h2o, x = list("ORGANIZATION_TYPE"), y = TARGET,
                                    target_encode_map = te_map, holdout_type = "None",
                                    fold_column = "fold",
                                    blended_avg = FALSE, noise_level = 0)

head(ext_valid_h2o[c("ORGANIZATION_TYPE", "TargetEncode_ORGANIZATION_TYPE")])
```

```{r}
ext_test_h2o <- h2o.target_encode_apply(test_h2o, x = list("ORGANIZATION_TYPE"), y = TARGET,
                                    target_encode_map = te_map, holdout_type = "None",
                                    fold_column = "fold",
                                    blended_avg = FALSE, noise_level = 0)

head(ext_test_h2o[c("ORGANIZATION_TYPE", "TargetEncode_ORGANIZATION_TYPE")])
```

Train model with KFold target encoding. Replace ORGANIZATION_TYPE with TargetEncode_ORGANIZATION_TYPE.

```{r}
y <- "TARGET"
x <- setdiff(names(ext_train_h2o), c(y,"ORGANIZATION_TYPE"))

automl_models_h2o <- h2o.automl(
    x = x,
    y = y,
    training_frame    = ext_train_h2o,
    validation_frame  = ext_valid_h2o,
    leaderboard_frame = ext_test_h2o,
    fold_column = "fold", # <<<check this when ready to run!!!
    max_runtime_secs  = 180
)
automl_leader <- automl_models_h2o@leader
```

```{r}
performance_h2o <- h2o.performance(automl_leader, newdata = test_h2o)
```

```{r}
performance_h2o %>%
    h2o.confusionMatrix()
```

```{r}
performance_h2o %>%
    h2o.auc()
```

```{r}
prediction_h2o <- h2o.predict(automl_leader, newdata = as.h2o(x_test_processed_tbl)) 

```

```{r}
prediction_tbl <- prediction_h2o %>%
    as.tibble() %>%
    bind_cols(
        x_test_processed_tbl %>% select(SK_ID_CURR)
    ) %>%
    select(SK_ID_CURR, p1) %>%
    rename(TARGET = p1)

prediction_tbl
```

```{r}
prediction_tbl %>%
    write_csv(path = "submission_003.csv")
```